\tw: a Xanalogical Storage and Authoring System

### 2003-02-15 papers/hypertext2003/paper.tex
Added more changes per Jim's comments.

We chose a filesystem backend, despite its scalability limitations, because of its simplicity.
This choice fits into our implementation philosophy, since the focus was on producing a working system and adding features iteratively.
A scalable backend might be seen as a feature to be added in a future iteration.
Our system, in its current form, is still functional in terms of its goal:  it can potentially support thousands of users and hundreds of thousands of documents, which is enough to give us an understanding of a xanalogical user experience.

@@

@@

For example, suppose that the balances of three users are as shown in following table:
%suppose user $A$ has a trial:real token balance of 50:200, user $B$ has a balance of 0:500, and user $C$ has a balance of 10:0.
\begin{center}
\begin{tabular}{|l||r|r|}
\hline
User&Trial balance &Real balance\\
\hline
$A$&50 &200\\
\hline
$B$&0  &500\\
\hline
$C$&10 &0  \\
\hline
\end{tabular}
\end{center}
Suppose that user $A$ reads a new 100-chracter document that is owned by $B$, but that the document contains a 20-character quote by $C$.
The resulting balances are shown in the following table:
\begin{center}
\begin{tabular}{|l||r|r|}
\hline
User&Trial balance &Real balance\\
\hline
$A$&0 &150\\
\hline
$B$&50  &530\\
\hline
$C$&10 &20  \\
\hline
\end{tabular}
\end{center}

@@

This two-type scheme allows users to try \tw \  extensively without a monetary investment, and it also poses no financial risks to the administrators.
Note that though trial tokens have no real-world value, they still have value in \tw, since they can always be used to purchase new content.
Inside \tw, a user that amasses many trial tokens is just as wealthy as a user that has many real tokens.
A user that actively published popular content in \tw \  could effectively use the system forever without depositing any real-world money.

>>>>

We chose a filesystem backend, despite its scalability limitations, because of its simplicity.
This choice fits into our implementation philosophy, since the focus was on producing a working system and adding features iteratively.
A scalable backend might be seen as a feature to be added in a future iteration.
Our system, in its current form, is still functional in terms of its goal, which is to support exploration of a multi-user xanalogical system.

@@

In our live system, we chose an exchange rate of 1,000,000 tokens for \$1, though this parameter can be changed on a site-by-site basis.
With this exchange rate, we tried to minimize financial burden on readers while still assigning appreciable value to content.
For example, the full text of this paper would cost about \$0.04, so 25 people would need to read it before it earned \$1 worth of tokens.

@@

For example, suppose that the balances of three users are as shown in following table:
%suppose user $A$ has a trial:real token balance of 50:200, user $B$ has a balance of 0:500, and user $C$ has a balance of 10:0.
\begin{center}
\begin{tabular}{|l||r|r|}
\hline
User&Trial balance &Real balance\\
\hline
$A$&50 &200\\
\hline
$B$&0  &500\\
\hline
$C$&10 &0  \\
\hline
\end{tabular}
\end{center}
Suppose that user $A$ reads a new 100-chracter document that is owned by $B$, but that the document contains a 20-character quote by $C$.
User $A$ must pay 100 tokens to access this new content, with 80 going to $B$ and 20 going to $C$.
The transfer logic favors trial tokens, so $A$'s trial balance is exhausted first by transfering 50 tokens to $B$.
The remaining payment to $B$ is made with 30 real tokens, and 20 real tokens are also transfered to $C$.
The resulting balances are shown in the following table:
\begin{center}
\begin{tabular}{|l||r|r|}
\hline
User&Trial balance &Real balance\\
\hline
$A$&0 &150\\
\hline
$B$&50  &530\\
\hline
$C$&10 &20  \\
\hline
\end{tabular}
\end{center}

@@

This two-type scheme allows users to try \tw \  extensively without a monetary investment, and it also poses no financial risks to the administrators.
Note that though trial tokens have no real-world value, they still have value in \tw, since they can always be used to purchase new content.
Inside \tw, a user that amasses many trial tokens is just as wealthy as a user that has many real tokens.
A user that actively publishes popular content in \tw \  could effectively use the system forever without depositing any real-world money.
